Carbon Nucleosynthesis

### 2023-04-04 thesis/tex/main.tex
thesis again

I also would not have made it here without all the additional support from my friends and family. Eric, even across the country, you have always been a point of support and stability, and I am always happy to be around you. Anya, you are a wonderful friend and I cannot thank you enough for your support this year. 
I love so many people in our department who have just been friends and positive support: Kaia, Maria, Autumn, Simon, Mary, Bailee, Aaliyah, Sanskruti, Alyssa, Harrison, Denis, and so many others. 
My Family (and Arya, my lovely labrodoodle).

@@

@@

    \includegraphics[scale=1]{y_agb_vs_z.pdf}
    \includegraphics[scale=1]{y_agb_vs_t.pdf}

@@

With uncertainties 

@@

While we show the entire dataset in Fig. \ref{fig:subgiants}, we chose to compare the
binned data to our models as black points with dashes representing the 1-sigma
spread, as in e.g. Fig. \ref{fig:agb_sims}.

@@

@@

We plot time evolution tracks in Fig. \ref{fig:c_evo} for \caah and \caafe for our fiducial model. Each colored track corresponds to a different galactic radius and 1Gyr time steps are marked with crosses on the lines.

Comparing [C/$\alpha$] against [Fe/H] enables us to see late time evolution of carbon more clearly. Because [Fe/H] takes longer to reach equilibrium as half of iron production comes from type-Ia supernovae, the late time evolution is not clustered as tightly horizontally as for [$\alpha$/H].

This is even more evident in the lower part of Fig. \ref{fig:c_evo}, where we
instead plot snapshots of the galactic radial trend at different times for our
model. While the \caah trend reaches almost equilibrium at 5Gyr, the \caafe trend continues to evolve even until the present day, exposing the effect of the delayed contribution from AGB stars on the evolutionary history.

\section{Effects of AGB Yields}

@@

\caption[AGB GCE Models]{Left: the \caah~ \textbf{median} present-day stellar tracks for four different
AGB models (\cristallo, \karakas, \kl, and \ventura ). The median bin [C/Mg] values from \citet{jack_subgiant} are
plotted as black points with 1-std errors marked by horizontal grey dashes.
Right: same as left but for \caafe. While each AGB yield model may
differ in detail, there is minimal effect on the overall [C/Mg] trends. }
\label{fig:agb_sims}
\end{figure}

@@

\section{Metallicity dependence and the AGB Fraction}

@@

\section{The AGB Fraction }
One potential tension with data is our models predict a low value for the AGB fraction of stars.

@@

\section{Star Formation History}

@@

\section{Outflows}
A common degeneracy in chemical evolution models is the yield-outflow degeneracy. An increase in stellar yields has a near-identical effect as a decrease in outflows. However, reducing the outflows reduces the evolution timescale of the system.

@@

\begin{figure*}
    \includegraphics[scale=0.9]{cooh_scatter.pdf}
    \includegraphics[scale=0.9]{cnoh_scatter.pdf}
    \caption[Scatter agreement]{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[]{summary-2.pdf}
\caption[Gas phase abundances]{Present-day gas phase tracks of the fiducial model in \caah~space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
\label{fig:gas_phase}
\end{figure*}

@@

>>>>

I also would not have made it here without all the additional support from my friends and family. Eric, even across the country, you have always been a point of support and stability, and I am always happy to be around you. Anya, you are a wonderful friend and I cannot thank you enough for your support this year. 
I love so many people in our department who have just been friends and positive support: Kaia, Maria, Autumn, Simon, Mary, Aaliyah, Sanskruti, Alyssa, Harrison, Denis, and so many others. 
My Family (and Arya, our lovely doodle).

@@

\begin{figure}
    \includegraphics[scale=1]{y_agb_t2.pdf}

    \caption[AGB DTD]{
    The Delay Time Distribution for AGB STars}

\end{figure}

@@

    \includegraphics[scale=1]{y_agb_vs_z.pdf}

@@

With uncertainties

@@

@@

Here, we present our fiducial model which we will later show aggrees well with APOGEE. We will later investigate the effects of alterations to this model.

In this model, we use the following yields:

@@

We plot time evolution tracks in Fig. \ref{fig:c_evo} for \caah and \caafe for our fiducial model. Comparing [C/$\alpha$] against [Fe/H] enables us to see late time evolution of carbon more clearly. Because [Fe/H] takes longer to reach equilibrium as half of iron production comes from type-Ia supernovae, the late time evolution is not clustered as tightly horizontally as for [$\alpha$/H].
This is even more evident in the lower part of Fig. \ref{fig:c_evo}. While the \caah trend reaches almost equilibrium at 5Gyr, the \caafe trend continues to evolve even until the present day, exposing the effect of the delayed contribution from AGB stars on the evolutionary history.

\begin{itemize}
    \item Describe definition of $f$ /etc.
    \item How we match the figures, DTD vs $\zeta$

\end{itemize}

@@

\caption[AGB GCE Models]{Left: the \caah~ \textbf{median} present-day stellar tracks for four different
AGB models (\cristallo, \karakas, \kl, and \ventura ). The median bin [C/Mg] values from \citet{jack_subgiant} are
plotted as black points with 1-std errors marked by horizontal grey dashes.
Right: same as left but for \caafe. While each AGB yield model may
differ in detail, there is minimal effect on the overall [C/Mg] trends.

While we show the entire dataset in Fig. \ref{fig:subgiants}, we chose to compare the
binned data to our models as black points with dashes representing the 1-sigma
spread, as in e.g. Fig. \ref{fig:agb_sims}. \label{fig:agb_sims}
}
\end{figure}

\section{Alternate Models}

@@

@@

One potential tension with data is our models predict a low value for the AGB fraction of stars.

@@

@@

\section{Outflows}

In GCE there are models requiring significant mass loading, but other approaches neglect outlows altogether. (Minchev, Chiappini and Martig (13, 14), Spitoni ++ 19,20,21).

We can modify our model to account for this by $\eta=0$.

A common degeneracy in chemical evolution models is the yield-outflow degeneracy. An increase in stellar yields has a near-identical effect as a decrease in outflows. However, reducing the outflows reduces the evolution timescale of the system.

@@

\begin{figure*}
    \centering
    \includegraphics[scale=0.9]{cooh_scatter.pdf}
    \caption[Scatter agreement]{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[]{summary.pdf}
\caption[Gas phase abundances]{Present-day gas phase tracks of the fiducial model in \caah~space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
\label{fig:gas_phase}
\end{figure*}

Carbon measurments in stars are difficult. There are measurments which can however be used to test.

We don't predict low metallicity but we are in agreement, substantial error bars.

Pop III stars from Cooke++.

@@

\begin{itemize}
    \item James ++23 Nitrogen,
    \item J++ found yield ratios, APOGEE -> yield assumptions
    \item SFH and eta don't matter too much.

        \item
        \item Variations in f and beta
        \item Evolutionary history
        \item Gas phase and Pop III
        \item Implications in Stellar evolution
        \item Continuing to work on neutron-capture e.t.c., 
        \item MWM and value of this work
\end{itemize}
